Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-23 Draft/draft.tex
Honghao: more completed draft

\newcommand{\ct}{^{\dagger}}
\newcommand{\tp}{^{\mathsf{T}}}

@@

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\calH}{\mathcal{H}}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}

@@

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle
%========================================
\section{Preliminaries and notations}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$.
We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.

\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, denoted by 
\begin{align}
\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
\end{align}
The superscript $(d)$ is to stress the local dimension and we follow this convention through this paper.

\textbf{The Pauli operators.} 
We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators behave like 
the $d$-dimensional Pauli operators which are defined by
\begin{align}
	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1}{i} \quad \pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i}
\end{align}
where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$,
for example, the addition above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
The weighted CHSH operator is defined as 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha(A_0B_0+A_0B_1) + A_1B_0 - A_1B_1,
\end{align}
where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respcetively.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, we have 
\begin{align}
	\bra{\phi} \I_\alpha \ket{\phi} \leq 2\alpha.
\end{align}
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
\bra{\psi} \I_\alpha \ket{\psi} \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation of \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz{2}$, $A_1 = \paulix{2}$,
	$B_0 = \cos(\mu) \pauliz{2} + \sin(\mu) \paulix{2}$ and $B_1 = \cos(\mu) \pauliz{2} - \sin(\mu) \paulix{2}$.
\end{definition}
We take an approach introduced in Ref.~\cite{bamps2015} and prove the following robust self-testing result.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ satisfies that
	\begin{align}
		\bra{\psi} \I_\alpha \ket{\psi} \geq 2\sqrt{1+\alpha^2} - \epsilon
	\end{align}
	for some $\alpha$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
	\end{align}
	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and where $A_x, B_y$ are from the 
	ideal strategy.
\end{theorem}
We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
After proving the robust the self-testing result, we take one step further and observed some interesting behaviour of the 
observable $\tilde{B}_0\tilde{B}_1$.
\begin{proposition}
\label{prop:2d-subspace}
	Suppose a quantum strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
	value of  $\bra{\psi}\I_{-\cot(\pi/2d)} \ket{\psi}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	By \cref{thm:selftest}, the condition that the strategy $(\ket{\psi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
	maximal value of $\bra{\psi}  \I_\alpha \ket{\psi} $ implies that there exists state $\ket{u_0}, \ket{u_1}$ such that 
	\begin{align*}
	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(\pi/2d) \ket{u_0} \\
	&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(\pi/2d) \ket{u_1}\\
	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = -2\sin(\pi/2d) \ket{u_1} \\
	&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = -2\sin(\pi/2d) \ket{u_0}.
	\end{align*}
	It is straightforward to calculate that 
	\begin{align}
		\tilde{B}_0\tilde{B}_1 \ket{u_0} &= \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1}\\
		\tilde{B}_0\tilde{B}_1\ket{u_1} &= \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1}.
	\end{align}
	We can conclude that 
	\begin{align}
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1})\\
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
	\end{align}
\end{proof}

\textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give answer for a chosen question. We denote Alice's question set by $X$ and answer set by $A$. Similarly,
Bob's question set is denoted by $Y$ and his answer set is denoted by $B$. The nonlocal game also
comes with two functions: $\pi: X \times Y \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: A \times B \times X \times Y \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new nonlocal game.

The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
by the conditional probability
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for } (a,b,x,y) \in A \times B \times X \times Y,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
The \emph{value} of a strategy is given by
\begin{align}
	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
\end{align}

The main contribution of our work is the construction of a nonlocal game $\G{d}$ that can be used to self-test $\ket{\EPR{d}}$where $d$ is an arbitrary odd prime number. 
In fact, our nonlocal game self-tests $\paulix{d}$ and $\pauliz{d}$ too, just implicitly.
The nonlocal game is a linear system game with modifications. 
We introduce the definition of self-testing first and then the definition of linear system game, 
which come from Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
\end{definition}
\begin{definition}[Linear system game]
 Let $Ax = b$ be an $m \times n$ linear system over $\Z_d$. The associated linear system game has two
 players Alice and Bob, where Alice is given a equation number $1 \leq x \leq m$ and replies with $a \in \Z_d^{\times n}$
 ,and Bob is given a variable $y$ and replies with an assignment $y \in \Z_d$. The winning condition is 
 \begin{align*}
 	a(y) &= b && \text{(Consistency)} \\
	\sum_{y = 1}^n A_{xy} a(y) &\equiv b(x) \pmod d. &&\text{(Constraint satisfaction)}
 \end{align*}
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
following group
\begin{align}
	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
See Appendix~\ref{sec:construct} for details about how to construct $\LS$.

The special property of $\Pg_{\LS}$ is summarized in the following lemma. 
\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		U = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && X = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices of the set $\{U^k X^l\}_{k \in[d-1]-1, l \in [d-1]}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1]-1, l \in [d-1]}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

>>>>

\newcommand{\ct}{^{\dagger}}
\newcommand{\tp}{^\intercal}

@@

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calX}{\mathcal{X}}
\newcommand{\calY}{\mathcal{Y}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\calB}{\mathcal{B}}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}

@@

\affil[1]{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA}
\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. Many copies of the $2$-dimensional EPR
pair can be self-tested in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but growing answer alphabet.

So far, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}
\label{thm:inf}
	There exists a set $D$ of odd prime numbers such that for any $d \in D$, 
	the maximally entangled state of local dimension $d$ can be self-tested 
	with constant question and answer sets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d$ whose primitive root is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}
\label{thm:pr_2}
	All maximally entangled state with local dimension $d$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
Note that although the sizes of the question and answer
sets do not depend on $d$, the optimal correlation does.
This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the game we designed consists of several sub-tests, we introduce the individual
sub-tests and their implications in \cref{sec:comp}. Our main result is based the combination
of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
our nonlocal game to self-test maximally entangled state of different dimensions.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.

\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, 
\begin{align}
\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
\end{align}
The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
which have operators of the similar form
\begin{align}
	X = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i} && U = \sum_{i=0}^{d-1} \ketbra{i/2}{i},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$.
for example, the $i/2$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
The weighted CHSH inequality is given below 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
\end{align}
where $A_x,B_y$ for $x,y = 0,1$ are Binary observables on Hilbert space $\calH_A$ and $\calH_B$ respectively.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
We take an approach introduced in Ref.~\cite{bamps2015} and prove the following robust self-testing result.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\alpha$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
	\end{align}
	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.
\end{theorem}
We defer the proof of \cref{thm:selftest} till Appendix~\ref{sec:selftest}.
After proving the robust the self-testing result, we take one step further and observe some interesting behaviour of the 
observable $\tilde{B}_0\tilde{B}_1$.
\begin{proposition}
\label{prop:2d-subspace}
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
	violation of  $\I_{\cot(-\pi/2d)}$, then there exists a $2$-dimensional Hilbert space which is spanned by eigenvectors of 
	$\tilde{B}_0\tilde{B}_1$ of eigenvalue $\omega_d$ and $\omega_d^{-1}$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_B(\ketbra{\tpsi}{\tpsi}))$ such that 
	\begin{align*}
	(\tilde{B}_0 + \tilde{B}_1) \ket{u_0} = 2\cos(-\pi/2d) \ket{u_0} 
	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_1} = -2\cos(-\pi/2d) \ket{u_1}\\
	(\tilde{B}_0 - \tilde{B}_1) \ket{u_0} = 2\sin(-\pi/2d) \ket{u_1} 
	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_1} = 2\sin(-\pi/2d) \ket{u_0}.
	\end{align*}
	It is straightforward to calculate that 
	\begin{align*}
		\tilde{B}_0\tilde{B}_1 \ket{u_0} = \cos(\pi/d) \ket{u_0} -\sin(\pi/d) \ket{u_1},&&
		\tilde{B}_0\tilde{B}_1\ket{u_1} = \sin(\pi/d)\ket{u_0} + \cos(\pi/d) \ket{u_1},
	\end{align*}
	so we can conclude that 
	\begin{align*}
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} + i\ket{u_1}) = e^{i \frac{\pi}{d}} (\ket{u_0} + i\ket{u_1}), &&
		&\tilde{B}_0\tilde{B}_1(\ket{u_0} - i\ket{u_1}) = e^{-i \frac{\pi}{d}} (\ket{u_0} - i\ket{u_1}).
	\end{align*}
	The actual eigenbasis we use is 
	\begin{align}
		\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
		\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1})
	\end{align}
	so that 
	\begin{align}
		&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
		&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1},
	\end{align}
	which is important for the whole embedding argument to work in \cref{sec:comp}.

\textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give ananswer for a chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new nonlocal game.

The quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side and 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. Then the behaviour of Alice and Bob is described 
by the conditional probability
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
The \emph{value} of a strategy is given by
\begin{align}
	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
\end{align}

The main contribution of our work is the construction of a nonlocal game $\G{d}$ with constant-sized $X$,$Y$,$A$ and $B$
that can be used to self-test $\ket{\EPR{d}}$ for arbitrary odd prime $d$. 
The nonlocal game is a linear system game with modifications or further enforcements. 
We introduce the definition of self-testing first and then the definition of linear system game, 
which come from Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
 and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
 \begin{align*}
 	a(y) &= b && \text{(Consistency)} \\
	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
 \end{align*}
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
\label{sec:comp}
%========================================
The goal of this section and the next section is to 
present a nonlocal game that can self-test $\ket{\EPR{d}}$, 
where $d$ is prime and has primitive root $2$\footnote{By $d$ has primitive root $2$,
we mean that $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.}
The game we constructed is denoted by $\G{d}$, which is the combination of several tasks.
In this section, we introduce such tests and their implications.
In \cref{sec:main}, we show how the implications can be combined to give a full self-test of $\ket{\EPR{d}}$. 
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
is included in the group $K$.
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
